Model LF

### 2023-03-16 paper version Hamid new test.Rmd
Commit

@@

COMMENT> 
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> SD1 >=1 & shock_wage_ds_model <= 0
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> TSLAG(wage_gap1,1) > max_gap & SD1 >=1 & shock_wage_ds_model > 0 
IDENTITY> wage_ds_t
EQ> wage_ds_t= max_dp/(1-max_gap)
IF> TSLAG(wage_gap1,1) <= max_gap & SD1 >=1 & shock_wage_ds_model > 0 
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD2 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD3 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD4 >= 1

@@

  shock_wage_ds_model  = TIMESERIES(c(shock_wage_ds_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4),
  emp_old = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
  emp_sens = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
   prod_ds_sens = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
    xk_ds_used = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  xk_ds_disc = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  sens1_up = TIMESERIES(c(sens1_up),   
                       START=c(2005,2),FREQ=4),
   sens1_low = TIMESERIES(c(sens1_low),   
                       START=c(2005,2),FREQ=4),
  sens2_up = TIMESERIES(c(sens2_up),   
                       START=c(2005,2),FREQ=4),
   sens2_low = TIMESERIES(c(sens2_low),   
                       START=c(2005,2),FREQ=4),
  sens_3 = TIMESERIES(c(sens_3),   
                       START=c(2005,2),FREQ=4),
  disc = TIMESERIES(c(disc),   
                       START=c(2005,2),FREQ=4)
  )
```

@@

#S_modelData$xk_ds_disc = xk_ds

@@

```{r}
###Gengivelse af stød til model
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_bs1 = Shock_bs1$simulation$yk
y_bs1 = Shock_bs1$simulation$y
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds
max_dp_bs1 = Shock_bs1$simulation$max_dp
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
xk_ds_bs1 = Shock_bs1$simulation$xk_ds
mk_ds_bs1 = Shock_bs1$simulation$mk_ds
lf_bs1 = Shock_bs1$simulation$lf
net_balance_bs1 = xk_ds_bs1 - mk_ds_bs1
net_balance_bs1_ratio= (xk_ds_bs1 - mk_ds_bs1)/yk_ds_bs1
nben_h_un_bs1 = Shock_bs1$simulation$nben_h_un
ur_bs1 = Shock_bs1$simulation$ur
s_g_bs1 = Shock_bs1$simulation$s_g
yh_g_bs1 = Shock_bs1$simulation$yh_g
i_g_bs1 = Shock_bs1$simulation$i_g
ik_bs1 = Shock_bs1$simulation$ik
mk_bs1 = Shock_bs1$simulation$mk
yd_g_bs1 = Shock_bs1$simulation$yd_g
tax_g_bs1 = Shock_bs1$simulation$tax_g
w_h_r_bs1 = Shock_bs1$simulation$w_h_r
tax_h_bs1 = Shock_bs1$simulation$tax_h
nben_g_bs1 = Shock_bs1$simulation$nben_g
ik_ratio_bs1 = ik_bs1/yk_ds_bs1
mk_ratio_bs1 = mk_bs1/yk_ds_bs1
c_ratio_bs1 = pconk_ds_bs1/yk_ds_bs1
gk_bs1 = Shock_bs1$simulation$gk

@@

```{r}
###Gengivelse af stød til model
max_dp_01 = Shock_1$simulation$max_dp
yk_ds_01 = Shock_1$simulation$yk_ds
wage_01 = Shock_1$simulation$wage
komp_r_01 = Shock_1$simulation$komp_r
part_01 = Shock_1$simulation$part
yk_01 = Shock_1$simulation$yk
pc_ds_01 = Shock_1$simulation$pc_ds
wage_ds_t_01 = Shock_1$simulation$wage_ds_t
ur_ds_01 = Shock_1$simulation$ur_ds
emp_01 = Shock_1$simulation$emp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
nben_h_un_01 = Shock_1$simulation$nben_h_un
lf_01 = Shock_1$simulation$lf
tilpas_pr_01 = Shock_1$simulation$tilpas_pr
u_ds_01 = Shock_1$simulation$u_ds
part_01 = Shock_1$simulation$part
nben_h_01 = Shock_1$simulation$nben_h
wage_ds_01 = Shock_1$simulation$wage_ds
dp_person_01 = Shock_1$simulation$dp_person
s_g_01 = Shock_1$simulation$s_g
ur_01 = Shock_1$simulation$ur
nl_g_01 = Shock_1$simulation$nl_g
unemp_01 = Shock_1$simulation$unemp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
wage_gap1_01 = Shock_1$simulation$wage_gap1
wage_gap_01 = Shock_1$simulation$wage_gap
prod_01 = Shock_1$simulation$prod
nben_g_01 = Shock_1$simulation$nben_g
yd_g_01 = Shock_1$simulation$yd_g
yh_g_01 = Shock_1$simulation$yh_g
tax_g_01 = Shock_1$simulation$tax_g
w_h_r_01 = Shock_1$simulation$w_h_r
tax_h_01 = Shock_1$simulation$tax_h
pconk_ds_01= Shock_1$simulation$pconk_ds
ik_01= Shock_1$simulation$ik
gk_01= Shock_1$simulation$gk
xk_ds_01= Shock_1$simulation$xk_ds
mk_ds_01= Shock_1$simulation$mk_ds

@@

```{r}
plot(window(lf_01 - lf_bs1, start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1");
legend("left", legend=c("Wages"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

@@

plot(window((abs(nben_h_un_01) - abs(nben_h_un_bs1)), start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

>>>>

wage_ben_gap= (wage_ds_bs1 - max_dp_bs1)

wage_ben_gap1= (wage_ds - obs_dp_q)/obs_dp_q

plot(wage_ben_gap)

alpha=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

@@

COMMENT> 
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> SD1 >=1 & shock_wage_ds_model <= 0
IDENTITY> wage_ds_t
EQ> wage_ds_t= alpha*wage_ds*(1+inflation_t) + (1-alpha)*max_dp*(1+wage_ben_gap)
IF> SD1 >=1 & shock_wage_ds_model > 0 
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD2 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD3 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD4 >= 1

COMMENT> 
IDENTITY> alpha
EQ> alpha = 1
IF> wage_ds*(1+inflation_t) >=  max_dp*(1+wage_ben_gap)
IDENTITY> alpha
EQ> alpha = 0
IF> wage_ds*(1+inflation_t) <  max_dp*(1+wage_ben_gap)

@@

  shock_wage_ds_model  = TIMESERIES(c(shock_wage_ds_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4),
  emp_old = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
  emp_sens = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
   prod_ds_sens = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
    xk_ds_used = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  xk_ds_disc = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  sens1_up = TIMESERIES(c(sens1_up),   
                       START=c(2005,2),FREQ=4),
   sens1_low = TIMESERIES(c(sens1_low),   
                       START=c(2005,2),FREQ=4),
  sens2_up = TIMESERIES(c(sens2_up),   
                       START=c(2005,2),FREQ=4),
   sens2_low = TIMESERIES(c(sens2_low),   
                       START=c(2005,2),FREQ=4),
  sens_3 = TIMESERIES(c(sens_3),   
                       START=c(2005,2),FREQ=4),
  disc = TIMESERIES(c(disc),   
                       START=c(2005,2),FREQ=4),
   alpha = TIMESERIES(c(alpha),   
                       START=c(2005,2),FREQ=4),
  wage_ben_gap = TIMESERIES(c(wage_ben_gap),   
                       START=c(2005,2),FREQ=4)
  )
```

@@

#S_modelData$wage_ben_gap = wage_ben_gap

@@

```{r}
###Gengivelse af stød til model
alpha_bs1 = Shock_bs1$simulation$alpha

wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t

wage_ds_bs1 = Shock_bs1$simulation$wage_ds

yk_ds_bs1 = Shock_bs1$simulation$yk_ds
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_bs1 = Shock_bs1$simulation$yk
y_bs1 = Shock_bs1$simulation$y
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds
max_dp_bs1 = Shock_bs1$simulation$max_dp
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
xk_ds_bs1 = Shock_bs1$simulation$xk_ds
mk_ds_bs1 = Shock_bs1$simulation$mk_ds
lf_bs1 = Shock_bs1$simulation$lf
net_balance_bs1 = xk_ds_bs1 - mk_ds_bs1
net_balance_bs1_ratio= (xk_ds_bs1 - mk_ds_bs1)/yk_ds_bs1
nben_h_un_bs1 = Shock_bs1$simulation$nben_h_un
ur_bs1 = Shock_bs1$simulation$ur
s_g_bs1 = Shock_bs1$simulation$s_g
yh_g_bs1 = Shock_bs1$simulation$yh_g
i_g_bs1 = Shock_bs1$simulation$i_g
ik_bs1 = Shock_bs1$simulation$ik
mk_bs1 = Shock_bs1$simulation$mk
yd_g_bs1 = Shock_bs1$simulation$yd_g
tax_g_bs1 = Shock_bs1$simulation$tax_g
w_h_r_bs1 = Shock_bs1$simulation$w_h_r
tax_h_bs1 = Shock_bs1$simulation$tax_h
nben_g_bs1 = Shock_bs1$simulation$nben_g
ik_ratio_bs1 = ik_bs1/yk_ds_bs1
mk_ratio_bs1 = mk_bs1/yk_ds_bs1
c_ratio_bs1 = pconk_ds_bs1/yk_ds_bs1
gk_bs1 = Shock_bs1$simulation$gk

@@

```{r}
###Gengivelse af stød til model
alpha_01 = Shock_1$simulation$alpha

max_dp_01 = Shock_1$simulation$max_dp
yk_ds_01 = Shock_1$simulation$yk_ds
wage_01 = Shock_1$simulation$wage
komp_r_01 = Shock_1$simulation$komp_r
part_01 = Shock_1$simulation$part
yk_01 = Shock_1$simulation$yk
pc_ds_01 = Shock_1$simulation$pc_ds
wage_ds_t_01 = Shock_1$simulation$wage_ds_t
ur_ds_01 = Shock_1$simulation$ur_ds
emp_01 = Shock_1$simulation$emp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
nben_h_un_01 = Shock_1$simulation$nben_h_un
lf_01 = Shock_1$simulation$lf
tilpas_pr_01 = Shock_1$simulation$tilpas_pr
u_ds_01 = Shock_1$simulation$u_ds
part_01 = Shock_1$simulation$part
nben_h_01 = Shock_1$simulation$nben_h
wage_ds_01 = Shock_1$simulation$wage_ds
dp_person_01 = Shock_1$simulation$dp_person
s_g_01 = Shock_1$simulation$s_g
ur_01 = Shock_1$simulation$ur
nl_g_01 = Shock_1$simulation$nl_g
unemp_01 = Shock_1$simulation$unemp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
wage_gap1_01 = Shock_1$simulation$wage_gap1
wage_gap_01 = Shock_1$simulation$wage_gap
prod_01 = Shock_1$simulation$prod
nben_g_01 = Shock_1$simulation$nben_g
yd_g_01 = Shock_1$simulation$yd_g
yh_g_01 = Shock_1$simulation$yh_g
tax_g_01 = Shock_1$simulation$tax_g
w_h_r_01 = Shock_1$simulation$w_h_r
tax_h_01 = Shock_1$simulation$tax_h
pconk_ds_01= Shock_1$simulation$pconk_ds
ik_01= Shock_1$simulation$ik
gk_01= Shock_1$simulation$gk
xk_ds_01= Shock_1$simulation$xk_ds
mk_ds_01= Shock_1$simulation$mk_ds

@@

```{r}
plot(window(tax_g_01 - tax_g_bs1, start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1");
legend("left", legend=c("Wages"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

@@

plot(window((abs(wage_ds_t_01) - abs(wage_ds_t_bs1)), start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```
